Rlearner_in_R

### 2025-07-15 codes/R/CF_Continuous_Loop.Rmd
minor edits

## Packages and functions
```{r}
#--- packages ---#
library(tidyverse)
library(data.table)
library(mgcv)
library(spatialsample)
library(parallel)
library(sf)
library(grf)
library(ranger)
library(xgboost)
library(mgcv)
#library(here)
library(reticulate)

#--- R functions ---#
here("Shared_codes/R") %>%
  fs::dir_ls(., full.names = TRUE) %>%
  lapply(source)

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)
py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")
source_python("Shared_codes/Python/run_CF_c.py")

```

@@

# load data only once, then drop
raw_sim_data <- readRDS("Data/raw_sim_data.rds")
rm(list = setdiff(ls(), c("raw_sim_data","np","run_CF_c_py","gm_wrapper_functions_you_need")))
gc()
```

@@

```{r}

x_vars <- c("Nk", "plateau", "b0")
T_formula <- yield ~ s(N, k = 4)

output_dir <- "Results/Seperate_Results/CF_in_R/all_sim_for_cf_5_fields"
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

@@

  tryCatch({
    # Train on five fields
    train_sim_ids <- sample(setdiff(1:500, test_sim_id), 5)
    sim_id_ls <- c(train_sim_ids, test_sim_id)

@@

    combined
  }, error = function(e) {
    message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
    return(data.table(sim = test_sim_id, aunit_id = integer(), opt_N_hat = numeric(), opt_N = numeric()))
  })
})
```

>>>>

## Packages and functions
```{r}
#--- packages ---#
library(tidyverse)
library(data.table)
library(mgcv)
library(spatialsample)
library(parallel)
library(sf)
library(grf)
library(ranger)
library(xgboost)
library(mgcv)
# library(here)
library(reticulate)

#--- R functions ---#
here("codes/R") %>%
  fs::dir_ls(., full.names = TRUE) %>%
  lapply(source)

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)
py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")
source_python("codes/Python/run_CF_c.py")
```

@@

# load data only once, then drop
raw_sim_data <- readRDS("data/raw_sim_data.rds")
rm(list = setdiff(ls(), c("raw_sim_data", "np", "run_CF_c_py", "gm_wrapper_functions_you_need")))
gc()
```

@@

```{r}
x_vars <- c("Nk", "plateau", "b0")
T_formula <- yield ~ s(N, k = 4)

output_dir <- "results/Seperate_Results/CF_in_R/all_sim_for_cf_5_fields"
output_dir <- "results/Seperate_Results/CF_in_R/all_sim_for_cf_5_fields"
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

@@

  tryCatch(
    {
      # Train on five fields
      train_sim_ids <- sample(setdiff(1:500, test_sim_id), 5)
      sim_id_ls <- c(train_sim_ids, test_sim_id)

@@

      combined
    },
    error = function(e) {
      message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
      return(data.table(sim = test_sim_id, aunit_id = integer(), opt_N_hat = numeric(), opt_N = numeric()))
    }
  )
})
```
